Linear regression for approximating real and synthetic data

### 2022-10-07 doc/paper.tex

\lstinputlisting[language=Python, firstline=27, lastline=42]{../../src/utils.py}

@@

\lstinputlisting[language=Python, firstline=238, lastline=245]{../../src/utils.py}

@@

\lstinputlisting[language=Python, firstline=53, lastline=64]{../../src/utils.py}

>>>>

\lstinputlisting[language=Python, firstline=27, lastline=42]{../src/utils.py}

@@

\lstinputlisting[language=Python, firstline=238, lastline=245]{../src/utils.py}

@@

\lstinputlisting[language=Python, firstline=53, lastline=64]{../src/utils.py}
